---
title: "Litorela"
author: "Pavel Jakubec"
date: "13. února 2016"
output:
  word_document: default
  pdf_document: default
  html_document:
    keep_md: yes
    theme: cerulean
---
# Litorela report  
## Effect of soil type on germination of Litorela uniflora   
```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2) # plotting graphs
library(Rmisc) # summarySE function for SE and CI calcul. and ploting
library (broom)
```

### Model:
* succ = number of germinated seeds  
* fail = succ - sum (all seeds)   
* treat = soil type  

```{r}
data=read.csv ("resubmision/prolicovani_ruzne_substraty_2.csv", header=TRUE, sep=";") 

```
```{r}
#put together some model
mod <- glm(cbind(succ, fail) ~ treat, data=data,family=binomial)
mod
summary(mod)
anova(mod, test="Ch")
```
### Results  
Vliv pudniho typu je vyznamny.  

### Residuals  
Residua se chovaji pomerne normalne, takze model fituje data dobre.  
```{r, error=FALSE}
#see what is going on with residuals
par(mfrow=c(2,2))
plot(mod)
par(mfrow=c(1,2))
rd=residuals(mod)
plot(rd)
qqnorm(residuals(mod, type="deviance"))
abline(a=0,b=1)
```


### Bar plot:   
```{r echo=FALSE}
#summary for ploting
sumary.dev = summarySE (data, 
  measurevar="succ", groupvars="treat")
sumary.dev$succ <- sumary.dev$succ*10
sumary.dev$se <- sumary.dev$se*10
sumary.dev <- sumary.dev[-(9),]

p = ggplot (sumary.dev, aes (y=succ, x=reorder(treat,succ)))
p2=p + stat_summary(fun.y=mean, geom="bar", position=position_dodge())+
  xlab("Germination substrate")+
  ylab("Mean germination (%)")+
  geom_errorbar(aes(ymin=succ-se, ymax=succ+se),
    width=.2,                    # Width of the error bars
    position=position_dodge(.9))
p3=p2+ coord_flip()
p3+scale_x_discrete(labels=c("Sand+Peat", "Sand+Clay","Peat", "Sand", "Clay", "Sand+Mud", "Mud", "Control"))

```

### Germination probability (%)   

```{r}
sumary.dev
rm(list=ls())
```
## THE END   

## Effect of place of origin on germination of Litorela uniflora   
```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2) # plotting graphs
library(Rmisc) # summarySE function for SE and CI calcul. and ploting
library (broom)
```

### Model:
* succ = number of germinated seeds    
* fail = succ - sum (all seeds)    
* loc = place of origin  
```{r, echo=F}
data=read.csv ("resubmision/kliceni_klima.csv", header=TRUE, sep=",") 
```
### Results

Vliv lokality ma vyznamny vliv na klicivost semen L. uniflora.  
```{r}
mod <- glm(cbind(succ, fail) ~ loc, data=data,family=binomial)
mod
summary(mod)
anova(mod, test="Ch")
```

### Residuals   

Residua se chovaji pomerne normalne, takze model fituje data dobre.   
```{r}
par(mfrow=c(2,2))
plot(mod)
par(mfrow=c(1,2))
rd=residuals(mod)
plot(rd)
qqnorm(residuals(mod, type="deviance"))
abline(a=0,b=1)

```


###Bar plot   
```{r, echo=FALSE, warning=FALSE, error=FALSE}
sumary.dev = summarySE (data, measurevar="succ", groupvars="loc")
sumary.dev$succ <- sumary.dev$succ/75*100
sumary.dev$se <- sumary.dev$se/75*100
sumary.dev <- sumary.dev[-(5),]


p = ggplot (sumary.dev, aes (y=succ, x=reorder(loc, succ)))
p + stat_summary(fun.y=mean, geom="bar", position=position_dodge())+
  xlab("Locality")+
  ylab("Mean germination (%)")+
  geom_errorbar(aes(ymin=succ-se, ymax=succ+se),
    width=.2,                    # Width of the error bars
    position=position_dodge(.9))


```
### Germination probability (%)   
Bohuzel netusim co ktery kod znamena, takze je to tam takto. Pripadalo mi to lepsi nez lok1-lokx.   
```{r}
sumary.dev
rm(list=ls())
```
### THE END  

## Germination under a layer of soil (climabox)   
```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2) # plotting graphs
library(Rmisc) # summarySE function for SE and CI calcul. and ploting
library (broom)
```

### Model:   
* succ = number of germinated seeds  
* fail = succ - sum (all seeds)  
* depth = soil layer depth  
```{r, echo=F}
substr=read.csv ("resubmision/proklicovani_klima.csv", header=TRUE, sep=",")  
```
### Results 
Vliv faktoru hloubka je vyznamny. 
```{r}
#put together some model
mod <- glm(cbind(succ, fail) ~ depth, data=substr,family=binomial)
mod
summary(mod)
anova(mod, test="Ch")
```

### Residuals  
Residua se chovaji pomerne normalne, takze model fituje data dobre.  
```{r, error=FALSE}
#see what is going on with residuals
par(mfrow=c(2,2))
plot(mod)
par(mfrow=c(1,2))
rd=residuals(mod)
plot(rd)
qqnorm(residuals(mod, type="deviance"))
abline(a=0,b=1)
```

### Barplot  
```{r, echo=FALSE, warning=FALSE, error=FALSE}
sumary.dev = summarySE (substr, measurevar="succ", groupvars="depth")
sumary.dev$succ <- sumary.dev$succ/75*100
sumary.dev$se <- sumary.dev$se/75*100


p = ggplot (sumary.dev, aes (y=succ, x=depth))
p + stat_summary(fun.y=mean, geom="bar", position=position_dodge())+
  xlab("Depth of substrate (cm)")+
  ylab("Mean germination (%)")+
  geom_errorbar(aes(ymin=succ-se, ymax=succ+se),
    width=.2,                    # Width of the error bars
    position=position_dodge(.9))+
  scale_x_continuous(breaks=c(0,1,3,5))


```
### Germination probability (%)
```{r}
sumary.dev
rm(list=ls())
```

###THE END   

##Germination under a layer of soil (glasshouse)   

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2) # plotting graphs
library(Rmisc) # summarySE function for SE and CI calcul. and ploting
library (broom)
```

### Model:
* y = number of germinated seeds  / number of fails  
* treat = soil layer depth  

```{r, echo=F}
data=read.csv ("resubmision/proklicovani_sklenik.csv", header=TRUE, sep=";") 
treat <- c(0,0,0,1,1,1,3,3,3,5,5,5)
germ <- apply(data[,3:18],1, sum)
length(germ)
total <- c(rep (25, 12))
p=germ/total #probability of succesfull germination
negative <- total-germ #how many did not germinate

data_glass<- data.frame (treat, germ, total, negative, p) # dataframe of resulting values
y<-cbind(germ, total - germ) # this vector should be feedid into binomial model
```
### Results   
Vliv faktoru hloubka je vyznamny.  
```{r}
#put together some model
m1=glm(y~treat, family=binomial)
m1
anova(m1, test="Ch")
summary(m1)
```
### Residuals   
Residua se chovaji divne. Asi schazi nejaky vysvetlujici faktor.
```{r, error=FALSE}
#see what is going on with residuals
par(mfrow=c(2,2))
plot(m1)
rd=residuals(m1,type = c("deviance"))
par(mfrow=c(1,2))
rd=residuals(m1)
plot(rd)
qqnorm(residuals(m1, type="deviance"))
abline(a=0,b=1)
```

### Barplot
```{r, echo=FALSE, warning=FALSE, error=FALSE}
sumary.dev = summarySE (data_glass, measurevar="germ", groupvars="treat")
sumary.dev$germ <- sumary.dev$germ/75*100
sumary.dev$se <- sumary.dev$se/75*100


p = ggplot (sumary.dev, aes (y=germ, x=treat))
p + stat_summary(fun.y=mean, geom="bar", position=position_dodge())+
  xlab("Depth of substrate (cm)")+
  ylab("Mean germination (%)")+
  geom_errorbar(aes(ymin=germ-se, ymax=germ+se),
    width=.2,                    # Width of the error bars
    position=position_dodge(.9))+
  scale_x_continuous (breaks=c(0,1,3,5))
```

### Germination probability (%)
```{r}
sumary.dev
rm(list=ls())
```